### 2021-01-25 README.Rmd
Added opening example

@@

# Visualizations (combined with patchwork pkg)
p1 <- autoplot(comp_bayes_lm_ex, type = "intercepts")
p2 <- autoplot(comp_bayes_lm_ex, type = "dbh_slopes")
p3 <- autoplot(comp_bayes_lm_ex, type = "competition")
(p1 | p2) / p3
```

>>>>

The starting point of our analysis are data from two repeat censuses `census_1_ex` and `census_2_ex`. For example consider the forest census data in `census_1_ex`

```{r}
census_1_ex
```

We convert the `census_1_ex` data frame to an object of type `sf` and then plot using `geom_sf()`.

```{r}
ggplot() +
  geom_sf(
    data = census_1_ex %>% sf::st_as_sf(coords = c("gx", "gy")),
    aes(col = sp, size = dbh)
  )
```

@@

# Posterior distributions (plots combined with patchwork pkg)
p1 <- autoplot(comp_bayes_lm_ex, type = "intercepts")
p2 <- autoplot(comp_bayes_lm_ex, type = "dbh_slopes")
p3 <- autoplot(comp_bayes_lm_ex, type = "competition")
(p1 | p2) / p3
```
